Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-09-10 paper/ms.tex
spergels orcid
abstract edits

\author{David N. Spergel}
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
  Princeton, NJ 08544, USA}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
  New York, NY 10010, USA}
\author{Justin Myles}
\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-precision radial velocity measurements.
  Stellar parameters determined from high-resolution Keck HIRES spectra
  indicate that both stars are $\sim 4$~Gyr old.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  % TODO: Hmmm...
  This is the largest and the most significant chemical difference found in
  a wide binary pair yet.
  Additionally, it shows an anomalously high surface lithium abundance
  ($A(\elem{Li})=2.75$), higher by $0.5$~dex than its companion.
  The proximity in phase-space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  We therefore suggest that the star HD~240430, ``Kronos'', accreted
  \maccreted\ of rocky material after birth selectively enhancing the
  refractory elements as well as lihtium in its surface and convective
  envelope.
\end{abstract}

>>>>

\author[0000-0002-5151-0006]{David N. Spergel}
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
  Princeton, NJ 08544, USA}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
  New York, NY 10010, USA}
\author{Justin Myles}
\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright solar-type
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars have an estimated 3D separation of $\approx 0.6$~pc ($\approx 0.01$~pc tangentially) at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-precision radial velocity measurements.
  Stellar parameters determined from high-resolution Keck HIRES spectra
  indicate that both stars are $\sim 4$~Gyr old.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex and a marginal
  enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  % TODO: Hmmm...
  This is the largest and the most significant chemical difference found in
  a wide binary pair yet.
  Additionally, HD~240430 shows an anomalously high surface lithium abundance
  ($A(\elem{Li})=2.75$), higher by $0.5$~dex than its companion.
  The proximity in phase-space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  We therefore suggest that the star HD~240430, ``Kronos'', accreted
  \maccreted\ of rocky material after birth, selectively enhancing the
  refractory elements as well as lithium in its surface and convective
  envelope.
\end{abstract}
